Visual Interrogation of Attention-Based Models: \\ Applications in Language Inference and Machine Comprehension

### 2018-05-28 EMNLP-demo-paper/system.tex
add back old perturbation

\section{System}
We design the visualization system with modularity and easy of use in mind.
%The initial learning curve and workflow setup cost of the tool are often the most significant barriers for user adaptation.
As a result, we designing the system as a Python library rather than as a monolithic standalone application. 
Just like a plotting library (i.e., matplotlib), the different pieces of the visualization (i.e., matrix based attention encoding) can be accessed individually, which helps ease the initial learning curve. 
The individual components can also be combined in any configuration desired by users via a simple API to better fit into one's workflow.
More importantly, the library-based design allows easy integration with the existing model implemented in Python.
%
To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as generating a prediction, accessing attention, to link the visualization to their NLP models.

@@

#open browser for visualization
modelVis.startServer()
\end{lstlisting}

\subsection{Attention Views}
As illustrated in Figure~\ref{fig:attention}(a)(b), the most widely adopted technique to bipartie graph

\subsection{Perturbation based exploration}
\label{sec:perturb}

>>>>

\section{System}

\subsection{Perturbation-Driven Exploration}
\label{sec:perturb}

\subsection{Attention Visualization}
As illustrated in Figure~\ref{fig:attention}(a)(b), the most widely adopted technique to bipartie graph

\subsection{Implementation}
The initial setup cost and learning curve of the tool are often the barriers for user adaptation. To address these challenge, we design the visualization system as a Python library with modularity and easy accessibility in mind.
Instead of using the visualization system as a monolithic standalone application, just like a plotting library (i.e., matplotlib), the different pieces of the visualization (i.e., matrix based attention encoding) can be accessed individually.
% 
Yet, the components can also be combined in any configuration desired by users via a simple API to better fit into one's workflow.
More importantly, the library-based design allows easy integration with the existing model implemented in Python.
%
To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as generating a prediction, accessing attention, to link the visualization to their NLP models. The the code required to create an interactive exploration environment for machine comprehension model is illustrated bellow.

@@

#open browser for the web-based interactive visualization
modelVis.show()
\end{lstlisting}
